% Created 2012-05-25 Fri 12:20
\documentclass[compress, 9pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\tolerance=1000
\usetheme{default}
\usecolortheme[RGB={0,38,93}]{structure}
\usefonttheme{serif}
\useinnertheme{circles}
\useoutertheme[]{shadow}
\setbeamertemplate{navigation symbols}{}
\usepackage{natbib}
\usepackage{fleqn}
\usepackage{epsf}
\usepackage[dvips]{color}
\usepackage{bibentry}
\institute{Computer Science and Engineering \\ University of Michigan}
\providecommand{\alert}[1]{\textbf{#1}}

\title{First-Order Logic}
\author{Shiwali Mohan}
\date{\today}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs Org-mode version 7.8.09}}

\begin{document}

\maketitle

\begin{frame}
\frametitle{Outline}
\setcounter{tocdepth}{3}
\tableofcontents
\end{frame}


\title[Search \hspace{1em}\insertframenumber/
\inserttotalframenumber]{Full Title}


\section{Translation}
\label{sec-1}
\begin{frame}
\frametitle{Translate the following sentences}
\label{sec-1-1}

\begin{itemize}
\item <1-> Every gardener likes the sun.
\begin{itemize}
\item <2-> $\forall$ x. gardener(x) $\Rightarrow$ likes(x,Sun)
\end{itemize}
\item <3-> You can fool some of the people all of the time.
\begin{itemize}
\item <4-> $\exists$ x. (person(x) $\wedge$ $\forall$ t.(time(t) $\Rightarrow$ can-fool(x,t)))
\end{itemize}
\item <5-> You can fool all of the people some of the time.
\begin{itemize}
\item <6-> $\forall$ x. (person(x) $\Rightarrow$ $\exists$ t. (time(t) $\wedge$ can-fool(x,t)))
\end{itemize}
\item <7-> All purple mushrooms are poisonous.
\begin{itemize}
\item <8-> $\forall$ x. (mushroom(x) $\wedge$ purple(x)) $\Rightarrow$ poisonous(x)
\end{itemize}
\item <9-> There are exactly two purple mushrooms.
\begin{itemize}
\item <10-> ($\exists$ x.$\exists$ y. mushroom(x) $\wedge$ purple(x) $\wedge$
    mushroom(y) $\wedge$ purple(y) $\wedge$ -(x=y)) $\wedge$ ($\forall$ z. (mushroom(z) $\wedge$ purple(z)) $\Rightarrow$ ((x=z) $\vee$ (y=z)))
\end{itemize}
\end{itemize}
\end{frame}
\section{Unification}
\label{sec-2}
\begin{frame}
\frametitle{Determine a valid substitution}
\label{sec-2-1}

\begin{itemize}
\item <1-> parents(x, father(x), mother(Bill));     parents(Bill, father(Bill), y)
\begin{itemize}
\item <2-> \{x/Bill, y/mother(Bill)\}
\end{itemize}
\item <3-> parents(x, father(x), mother(Bill));     parents(Bill, father(y), z)
\begin{itemize}
\item <4-> \{x/Bill, y/Bill, z/mother(Bill)\}
\end{itemize}
\item <5-> parents(x, father(x), mother(Jane));     parents(Bill, father(y), mother(y))
\begin{itemize}
\item <6-> Failure
\end{itemize}
\end{itemize}
\end{frame}
\section{CNF conversion}
\label{sec-3}
\begin{frame}
\frametitle{Convert to CNF}
\label{sec-3-1}

$\forall$ x.(P(x) $\Rightarrow$ ($\forall$ y.(P(y) $\Rightarrow$ P(f(x,y))) $\wedge$ -$\forall$ y.(Q(x,y) $\Rightarrow$ P(y))))
\begin{itemize}
\item <2-> Eliminate implication
\begin{itemize}
\item <3-> $\forall$ x.(-P(x) $\vee$ ($\forall$ y.(-P(y) $\vee$ P(f(x,y))) $\wedge$ -$\forall$ y.(-Q(x,y) $\vee$ P(y))))
\end{itemize}
\item <4-> Move - inwards
\begin{itemize}
\item <5-> $\forall$ x.(-P(x) $\vee$ ($\forall$ y.(-P(y) $\vee$ P(f(x,y))) $\wedge$ $\exists$ y.(Q(x,y) $\wedge$ -P(y))))
\end{itemize}
\item <6-> Standardize Variables
\begin{itemize}
\item <7-> $\forall$ x.(-P(x) $\vee$ ($\forall$ y.(-P(y) $\vee$ P(f(x,y))) $\wedge$ $\exists$ z.(Q(x,z) $\wedge$ -P(z))))
\end{itemize}
\item <8-> Skolemize
\begin{itemize}
\item <9-> $\forall$ x.(-P(x) $\vee$ ($\forall$ y.(-P(y) $\vee$ P(f(x,y))) $\wedge$ (Q(x,g(x)) $\wedge$ -P(g(x)))))
\end{itemize}
\item <10-> Drop universal
\begin{itemize}
\item <11->(-P(x) $\vee$ ((-P(y) $\vee$ P(f(x,y))) $\wedge$ (Q(x,g(x)) $\wedge$ -P(g(x)))))
\end{itemize}
\item <12-> Distribute `or' over `and'
\begin{itemize}
\item <13-> (-P(x) $\vee$ -P(y) $\vee$ P(f(x,y))) $\wedge$ (-P(x) $\vee$ Q(x,g(x)))
    $\wedge$ (-P(x) v -P(g(x))
\end{itemize}
\item <14-> Create separate clauses
\begin{itemize}
\item <15-> -P(x) $\vee$ -P(y) $\vee$ P(f(x,y))
\item <15-> -P(x) $\vee$ Q(x,g(x))
\item <15-> -P(x) $\vee$ -P(g(x))
\end{itemize}
\item <16-> Standardize variables
\begin{itemize}
\item <16-> -P(x) $\vee$ -P(y) $\vee$ P(f(x,y))
\item <16-> -P(z) $\vee$ Q(z,g(z))
\item <16-> -P(w) $\vee$ -P(g(w))
\end{itemize}
\end{itemize}
\end{frame}
\section{FOL Resolution}
\label{sec-4}
\begin{frame}
\frametitle{Resolution by Refutation}
\label{sec-4-1}

\textbf{Knowledge Base}: \\
Tony, Sam and Ellen belong to the Activity Club. Every member of the
Activity Club is either a skier or a mountain climber or both. No mountain
climber likes rain, and all skiers like snow. Ellen dislikes whatever
Tony likes and likes everything that Tony dislikes. Tony likes rain and snow.
\\
\\

\textbf{Question}: \\
Which member of the Activity Club is a mountain climber but not a skier?
\end{frame}
\begin{frame}
\frametitle{Translate to FOL Sentences}
\label{sec-4-2}

member(x) means is a member of activity club, S(x) means x is a skier, M(x) means x is a mountain climber, and L(x,y) means x likes y
\begin{itemize}
\item Every member of the Activity Club is either a skier or a mountain
  climber or both.
\begin{itemize}
\item <2-> $\forall$ x. member(x) $\Rightarrow$ (S(x) $\vee$ M(x))
\end{itemize}
\item No mountain climber likes rain
\begin{itemize}
\item <3-> -$\exists$ x. M(x) $\wedge$ L(x, Rain)
\end{itemize}
\item All skiers like snow.
\begin{itemize}
\item <4->  $\forall$ x. S(x) $\Rightarrow$ L(x, Snow)
\end{itemize}
\item Tony, Sam and Ellen belong to the Activity Club.
\begin{itemize}
\item <5-> member(Tony)
\item <5-> member (Sam)
\item <5-> member (Ellen)
\end{itemize}
\item Ellen dislikes whatever Tony likes and likes everything that Tony dislikes.
\begin{itemize}
\item <6-> $\forall$ y. L(Ellen, y) $\Leftrightarrow$ -L(Tony, y)
\end{itemize}
\item Tony likes rain and snow.
\begin{itemize}
\item <7-> L(Tony, Rain)
\item <7-> L(Tony, Snow)
\end{itemize}
\item Which member of the Activity Club who is a mountain climber but not
  a skier?
\begin{itemize}
\item <8-> Query ($\exists$ x. member(x) $\wedge$ M(x) $\wedge$ -S(x))
\item <8-> Negation of the Query or Answer literal (-$\exists$
    x. member(x) $\wedge$ M(x) $\wedge$ -S(x)) $\vee$ Ans(x)
\end{itemize}
\end{itemize}
\end{frame}
\begin{frame}
\frametitle{CNF}
\label{sec-4-3}

\hspace{0}

\begin{center}
\begin{tabular}{ll}
 $\forall$ x. member(x) $\Rightarrow$ S(x) $\vee$ M(x)                 &  1. -member(x1) $\vee$ S(x1) $\vee$ M(x1)  \\
 -$\exists$ x. M(x) $\wedge$ L(x, Rain)                                &  2. -M(x2) $\vee$ -L(x2, Rain)             \\
 $\forall$ x. S(x) $\Rightarrow$ L(x, Snow)                            &  3. -S(x3) $\vee$ L(x3, Snow)              \\
 member(Tony)                                                          &  4. member(Tony)                           \\
 member (Sam)                                                          &  5. member(Sam)                            \\
 member (Ellen)                                                        &  6. member(Ellen)                          \\
 $\forall$ y. L(Ellen, y) $\Leftrightarrow$ -L(Tony, y)                &  7. -L(Tony, x4) $\vee$ -L(Ellen, x4)      \\
                                                                       &  8. L(Tony, x5) $\vee$ L(Ellen, x5)        \\
 L(Tony, Rain)                                                         &  9. L(Tony, Rain)                          \\
 L(Tony, Snow)                                                         &  10. L(Tony, Snow)                         \\
 (-$\exists$ x. member(x) $\wedge$ M(x) $\wedge$ -S(x)) $\vee$ Ans(x)  &  11. (-member(x7) $\vee$ -M(x7)            \\
                                                                       &  $\vee$ S(x7) $\vee$ Ans(x7)               \\
\end{tabular}
\end{center}
\end{frame}
\begin{frame}
\frametitle{Resolution}
\label{sec-4-4}

\begin{enumerate}
\item -member(x1) $\vee$ S(x1) $\vee$ M(x1)
\item -M(x2) $\vee$ -L(x2, Rain)
\item -S(x3) $\vee$ L(x3, Snow)
\item member(Tony)
\item member(Sam)
\item member(Ellen)
\item -L(Tony, x4) $\vee$ -L(Ellen, x4)
\item L(Tony, x5) $\vee$ L(Ellen, x5)
\item L(Tony, Rain)
\item L(Tony, Snow)
\item (-member(x7) $\vee$ -M(x7) $\vee$ S(x7)) $\vee$ Ans(x7)
\item <2-> S(x1) $\vee$ (-member(x1) $\vee$ Ans(x1)) [11,1]      \{x7/x1\}
\item <3-> L(x1, Snow) $\vee$ (-member(x1) $\vee$ Ans(x1)) [12,3] \{x3/x1\}
\item <4-> -L(Tony, Snow) $\vee$ (-member(Ellen) $\vee$ Ans(Ellen)) [13,7] \{x4/Snow, x1/Ellen\}
\item <5-> -member(Ellen) v Ans(Ellen) [14,7] \{\}
\item <6 -> Ans(Ellen) [15,6] \{\}
\end{enumerate}
\end{frame}

\end{document}
